### 2016-05-11 README.Rmd
updated README
removed call to `svglite` and updated some of the statuses

---
output:
  md_document:
    variant: markdown_github
---

@@

library(svglite)

@@

```{r vis_dat}
library(visdat)

@@

At the moment `vis_guess` is slow as - take this into consideration when you are using it on data with more than 1000 rows. We're looking into ways of making it faster, potentially using methods from the `parallel` package, or writing some c++ code.

# Future work

@@

Another idea is to pass expectations into `vis_dat` or `vis_miss`, along the lines of the `expectation` command in `assertr`. For example, you could ask `vis_dat` to identify those cells with values of -1 with something like this:

@@

`vis_datly`. `vis_dat` could include an interactive version of the plots using `plotly`, so that you can actually _see_ what is inside the data.

@@

Thanks also to Noam Ross for his suggestions and code for using plotly with visdat.

>>>>

---
output:
  md_document:
    variant: markdown_github
always_allow_html: yes
---

@@

@@

```{r vis_dat}

library(visdat)

@@

At the moment `vis_guess` is very slow. Please take this into consideration when you are using it on data with more than 1000 rows. We're looking into ways of making it faster, potentially using methods from the `parallel` package, or extending the c++ code from `readr:::collectorGuess`.

# Interactivity

Thanks to Carson Sievert, you can now add some really nifty interactivity into visdat by using `plotly::ggplotly`, allowing for information to be revealed upon mouseover of a cell. For example:

library(plotly)

vis_dat(example2) %>% ggplotly()

# Road Map

**Allowing for missings to be visualised/seen when there is a small proportion**

This problem will be approached by adding in a bar at the top of the visualisation that indicates whether there are any missings in a column. I will also add into the legend the % of overall missing/absent.

@@

The idea here is to pass expectations into `vis_dat` or `vis_miss`, along the lines of the `expectation` command in `assertr`. For example, you could ask `vis_dat` to identify those cells with values of -1 with something like this:

@@

@@

Thanks also to Carson Sievert for writing the code that combined plotly with visdat, and for Noam Ross for suggesting this in the first place.
